\cvsection{Education}
\begin{cventries}
  \cventry
    {Computer Science MEng Hons. \textbf{First Class with Dean's List Award}} % Degree
    {University of Southampton} % Institution
    {Southampton} % Location
    {October 2018 - 2022 } % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Year 1:} Excelled in Programming I and II, mastering Object-Oriented concepts in Java (scores: 80\% and 84\%). Achieved 100\% in Data Management coursework demonstrating proficiency in Git Version Control. Overall first-year module average: 75\%.}
        \vspace{0.5mm}
        \item {\textbf{Year 2:} Explored Functional Programming in Haskell, including developing a unique programming language. Delved into Theory of Computing and Interaction Design.}
        \item {\textbf{Year 3:} Secured a First-Class Mark in Dissertation focused on software standards using Rust Programming Language. Advanced in Natural Language Processing, Machine Learning Technologies, and Web Infrastructure (\textbf{95\% on a coursework involving HTML and CSS}). Yearly average: 82.5\%.}
        \item {\textbf{Year 4:} Completed a Master's Dissertation on Trend Detection at Scale. Gained knowledge in Computational Finance, Software Security, and Project Management (PMBOK). Achieved a yearly average of \textbf{80.7\%} and was honoured with the \textbf{Dean's List Award} for outstanding academic performance.}
      \end{cvitems}
    }
  \cventry
    {}
    {Oakwood Park Grammar School}
    {Maidstone}
    {2011-2018}
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{GCSE:} Achieved nine A* grades, including Mathematics, Computing, and French, plus three A grades.}
        \vspace{0.5mm}
        \item {\textbf{A-Level:} Attained A* grades in Mathematics and Further Mathematics, and an A in English Language. Excelled in the Extended Project Qualification with an A*, creating a polling website using the \textbf{Laravel} framework. Received two subject awards, a distinction shared with only one other student.}
      \end{cvitems}
    }
\end{cventries}

