\cvsection{Experience}
\begin{cventries}
    \cventry
    {Software Engineer} % Job title
    {RDT Limited} % Organization
    {Maidstone, UK} % Location
    {Jan 2024 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Developing and deploying web-based applications using \textbf{.NET} and \textbf{Blazor} \textbf{(C\#)}, with a strong focus on \textbf{Test-Driven Development (TDD)}, \textbf{API design}, and best coding practices.}
        \item {Taking ownership of features, independently driving development, testing, and deployment while collaborating with cross-functional teams to ensure smooth releases.}
        \item {Contributing to \textbf{open-source projects} such as \textbf{Blazorise} to accelerate internal development, submitting pull requests to unblock dependencies.}
        \item {Actively involved in \textbf{mentoring} and \textbf{recruitment}—reviewing code submissions, providing feedback, and representing the company at career fairs to attract new talent.}
        \item {\textbf{Leading} daily standups, facilitating team discussions, and ensuring effective \textbf{cross-team collaboration} to maintain alignment and productivity.}
      \end{cvitems}
    }
    \\[15pt]
    \cventry
    {Associate Software Engineer} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item {Delivered high-quality PBIs for web applications, mastering \textbf{.NET} and \textbf{Blazor}, and implementing features from design to deployment.}
        \item {Spearheaded \textbf{Infrastructure as Code (IaC)} using \textbf{Terraform} and optimized Azure DevOps pipelines for a critical project.}
        \item {\textbf{Mentored} apprentices and new hires, guiding them through feature development, testing, and best practices in code quality.}
        \item {Gained \textbf{AZ-900 Azure Fundamentals} certification from \textbf{Microsoft}}
        \item {\textbf{Promoted} to Software Engineer after one year}
      \end{cvitems}
    }
    \\[20pt]
    \cventry
    {Bioinformatician Degree Apprentice (Lvl 7)} % Job title
    {AstraZeneca} % Organization
    {Cambridge, UK} % Location
    {Sept 2022 - Sept 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Developed and optimized algorithms for drug discovery using \textbf{Rust}, and performed data analysis with \textbf{Python} and \textbf{R}.}
        \item {Used \textbf{Kubeflow} for scalable remote analysis of large datasets in cloud environments.}
        \item {Adapted quickly to new languages like \textbf{R}, delivering coursework within tight deadlines while working full-time.}
        \item {Gained experience with \textbf{Linux} system management and \textbf{Java} for application development.}
        \item {Completed training in time management and presentation skills to improve technical communication.}
      \end{cvitems}
    }
    \\[15pt]
    \cventry
    {Student Demonstrator - Agile Workflow} % Job title
    {University of Southampton} % Organization
    {Southampton, UK} % Location
    {Feb - May 2022} % Date(s)
    {
      \begin{cvitems}
        \item {Mentored and guided student teams in \textbf{Agile development}, overseeing the creation of \textbf{Java}-based applications.}
        \item {Led review meetings, provided technical feedback, and acted as a bridge between students and faculty.}
      \end{cvitems}
    }
\end{cventries}
